### 2012-07-23 docs/mg/mg.tex
intro stub
note about MG
add HG centeringsadd HG centeringsadd HG centeringsadd HG centeringsadd HG centeringsadd HG centeringsadd HG centeringsadd HG centeringsadd HG centerings

@@

>>>>

\section{Introduction to \maestro\ Multigrid}

\maestro\ uses multigrid to enforce the velocity constraint through
projections at the half-time (the MAC projection) and end of the time
step.  Two multigrid solvers are provided by \boxlib---one for
cell-centered data and one for node-centered (nodal) data.

\begin{figure}[t]
\centering
\includegraphics[width=5.5in]{MAC_mg2}
\caption{\label{fig:mg:MAC} Data centerings for the MAC projection}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=5.5in]{HG_mg2}
\caption{\label{fig:mg:HG} Data centerings for the HG projection}
\end{figure}

\section{\mgtower}

The \mgtower\ is a special Fortran derived type that carries all the
information required for a \boxlib\ multigrid solve.

\section{Bottom Solvers}

\section{Convergence Criteria}

@@

\label{sec:mgtol}
